\begin{flushleft} \textsf{\small Statistics and Computing} \end{flushleft} \vspace{0.5cm} Supplementary material for "Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming"

### 2021-02-11 Paper/online_supplemental_material/online_supplemental_material.tex
update bib path in suplemental material

\author{Gabriel Riutort-Mayol$^{1*}$, Paul-Christian Bürkner$^2$, Michael R.\ Andersen$^{3}$,\\
  Arno Solin$^{2}$, Aki Vehtari$^{2}$}

\date{ \small
$^1$ Department of Cartographic Engineering, Geodesy, and Photogrammetry, Universitat Polit\`ecnica de Val\`encia, Spain 
\break
$^2$ Department of Computer Science, Aalto University, Finland
\break
$^3$ Department of Applied Mathematics and Computer Science, Technical University of Denmark, Denmark
\break
$^*$ Corresponding author, Email: gabriuma@gmail.com
}

@@

\bibliography{../manuscript_v2/references}

>>>>

\author{Gabriel Riutort-Mayol$^{1*}$, Paul-Christian Bürkner$^2$, Michael R.\ Andersen$^{3}$,\\
  Arno Solin$^{4}$, Aki Vehtari$^{4}$}

\date{ \small
$^1$ Department of Cartographic Engineering, Geodesy, and Photogrammetry, Universitat Polit\`ecnica de Val\`encia, Spain 
\break
$^2$ Excellence Cluster for Simulation Technology, University of Stuttgart, Germany
\break
$^3$ Department of Applied Mathematics and Computer Science, Technical University of Denmark, Denmark
\break
$^4$ Department of Computer Science, Aalto University, Finland
\break
$^*$ Corresponding author, Email: gabriuma@gmail.com
}

@@

\bibliography{../Manuscript_Stats&Comp/references}
